The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-07-02 SC-challenge.tex
shortened a few more places
Reduced CodeMeta author list to just Carli and others. Sorry, Matt...

\begin{bottomstuff}
Work by K.\ E.\ Niemeyer was supported in part by the National Science Foundation (NSF) under grant ACI-1535065.
Work by D.\ S.~Katz was supported by the NSF while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University;
A.\ M.\ Smith,
GitHub, Inc.;
D.\ S.\ Katz,
NCSA \& iSchool \& ECE, University of Illinois at Urbana--Champaign;
emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
\end{bottomstuff}

@@

However, research and development efforts are needed to solve the remaining challenges.
These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the software itself is not publicly preserved?
Software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation, so how can index services be encouraged to fully index software?
How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors---should such a citation be ``weighted'' higher than others?
The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.

>>>>

\begin{bottomstuff}
Work by K.\ E.\ Niemeyer was supported in part by the National Science Foundation (NSF) under grant ACI-1535065.
Work by D.\ S.~Katz was supported by the NSF while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
Author's addresses: K.\ E.\ Niemeyer, School of MIME, Oregon State University;
A.\ M.\ Smith,
GitHub, Inc.;
D.\ S.\ Katz,
NCSA \& iSchool \& ECE, University of Illinois at Urbana--Champaign;
emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
\end{bottomstuff}

@@

Research and development efforts are needed to solve the remaining challenges.
These include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the software itself is not publicly preserved?
Software citations require indexing to create a citation network akin to publications to carry weight for academic credit and reputation, so how can index services be encouraged to fully index software?
How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors---should such a citation be ``weighted'' higher than others?
The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.
